He-Man: A domain-specific language for lightweight concurrency

### 2012-03-02 paper/paper.tex
add some notes to the paper tex

\begin{abstract}
We present He-Man, a compiled, embedded, domain specific language in Haskell for
building scalable network applications in a natural, straight-line manner while
still producing efficient event loop-based code. He-Man programs are compact and
measurements indicate that it performs acceptably. Our implementation is
available at
\url{https://github.com/msullivan/networks-project}.
\end{abstract}

@@

\section{Related work}

@@

The He-Man runtime is written in C and provides a state machine based
thread scheduling model. In the view of the runtime, a thread consists
of some bookkeeping state, some private state, and the next
continuation function the thread is to run. The main part of the
runtime's state consists of the runqueue, which contains a list of all
currently runnable threads.

@@

The He-Man runtime main loop is very simple, then: it loops
indefinitely, and on each iteration it removes the thread at the head
of the runqueue (if it exists) and runs it, and polls for I/O events.

@@

The runtime also has support for Linux Kernel Asynchronous IO for file
IO, using a Linux \t{eventfd} to allow \t{epoll} to wait on AIO
events. This support is currently unused, since it was not actually
necessary to acheive acceptable performance for the web server.

@@

To evaluate He-Man, we built two network applications with He-Man and
compared them to similar network applications built in C.
We also discuss He-Man's memory overhead.

@@

\section{Future work}

>>>>

% TODO: talk about type system, runtime improvements, optimizations

\begin{abstract}
% XXX: better abstract;
% and where should we put the code link?
% we should also move it to some better URL

We present He-Man, a compiled, embedded, domain specific language in Haskell for
building scalable network applications in a natural, straight-line manner while
still producing efficient event loop-based code. He-Man programs are compact and
measurements indicate that it performs acceptably. Our implementation is
available at
\url{https://github.com/msullivan/networks-project}.
\end{abstract}

@@

%% XXX: Should we put this at the end?
\section{Related work}

@@

%% XXX: update
The He-Man runtime is written in C and provides a state machine based
thread scheduling model. In the view of the runtime, a thread consists
of some bookkeeping state, some private state, and the next
continuation function the thread is to run. The main part of the
runtime's state consists of the runqueue, which contains a list of all
currently runnable threads.

@@

% XXX: this has changed
The He-Man runtime main loop is very simple, then: it loops
indefinitely, and on each iteration it removes the thread at the head
of the runqueue (if it exists) and runs it, and polls for I/O events.

@@

% XXX: this is not quite true; also who cares?
The runtime also has support for Linux Kernel Asynchronous IO for file
IO, using a Linux \t{eventfd} to allow \t{epoll} to wait on AIO
events. This support is currently unused, since it was not actually
necessary to acheive acceptable performance for the web server.

@@

To evaluate He-Man, we built several network applications with He-Man
and compared them to similar network applications built in C.  We also
discuss He-Man's memory overhead.

@@

%% XXX: needs serious work
\section{Future work}
